### 2013-06-10 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
adding solver verification data for serial flux calculations

Table~\ref{tab:serial_differences} gives the maximum and minimum
absolute differences for all calculations and all energy groups using
the BiCGStab calculation as the reference. All comparisons were
performed within a group such that the MCSA-ILUT-R-C results in group
3 for the 4-group calculation were computed with the BiCGStab-ILUT
solution in group 3 for the 4-group calculation as a reference.

>>>>

Table~\ref{tab:serial_differences_g1},
Table~\ref{tab:serial_differences_g2}, and
Table~\ref{tab:serial_differences_g4} give the maximum and minimum
absolute differences for all calculations and all energy groups using
the BiCGStab calculation as the reference. All comparisons were
performed within a group such that the MCSA-ILUT-R-C results in group
3 for the 4-group calculation were computed with the BiCGStab-ILUT
solution in group 3 for the 4-group calculation as a reference.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{Minimum Difference}} &
      \multicolumn{1}{c}{\textbf{Maximum Difference}} \\
      \hline
      GMRES-ILUT & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-R-C & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-MR-C & 0 & 0.0 & \sn{2.205}{-9} \\
      MCSA-ILUT-R-EV & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-MR-EV & 0 & 0.0 & \sn{9.313}{-10} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      1-group fuel assembly problem.} \textit{The maximum and minimum
      absolute differences over the entire spatial domain are
      presented with BiCGStab used as the reference. Each calculation
      was converged with the same eigensolver and linear solver
      tolerances.}}
  \label{tab:serial_differences_g1}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{Minimum Difference}} &
      \multicolumn{1}{c}{\textbf{Maximum Difference}} \\
      \hline
      GMRES-ILUT & 0 & 0.0 & \sn{2.794}{-9} \\
      MCSA-ILUT-R-C & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-MR-C & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-R-EV & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-MR-EV & 0 & 0.0 & \sn{9.313}{-10} \\
      \hline
      GMRES-ILUT & 1 & 0.0 & \sn{4.657}{-10} \\
      MCSA-ILUT-R-C & 1 & 0.0 & \sn{1.364}{-10} \\
      MCSA-ILUT-MR-C & 1 & 0.0 & \sn{1.261}{-9} \\
      MCSA-ILUT-R-EV & 1 & 0.0 & \sn{2.474}{-10} \\
      MCSA-ILUT-MR-EV & 1 & 0.0 & \sn{5.857}{-10} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      2-group fuel assembly problem.} \textit{The maximum and minimum
      absolute differences over the entire spatial domain are
      presented with BiCGStab used as the reference. Each calculation
      was converged with the same eigensolver and linear solver
      tolerances.}}
  \label{tab:serial_differences_g2}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{Minimum Difference}} &
      \multicolumn{1}{c}{\textbf{Maximum Difference}} \\
      \hline
      GMRES-ILUT & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-R-C & 0 & 0.0 & \sn{1.397}{-9} \\
      MCSA-ILUT-MR-C & 0 & 0.0 & \sn{1.870}{-9} \\
      MCSA-ILUT-R-EV & 0 & 0.0 & \sn{1.397}{-9} \\
      MCSA-ILUT-MR-EV & 0 & 0.0 & \sn{1.869}{-9} \\
      \hline
      GMRES-ILUT & 1 & 0.0 & \sn{5.821}{-11} \\
      MCSA-ILUT-R-C & 1 & 0.0 & \sn{1.164}{-10} \\
      MCSA-ILUT-MR-C & 1 & 0.0 & \sn{1.164}{-10} \\
      MCSA-ILUT-R-EV & 1 & 0.0 & \sn{1.164}{-10} \\
      MCSA-ILUT-MR-EV & 1 & 0.0 & \sn{1.164}{-10} \\
      \hline
      GMRES-ILUT & 2 & 0.0 & \sn{1.164}{-10} \\
      MCSA-ILUT-R-C & 2 & 0.0 & \sn{2.328}{-10} \\
      MCSA-ILUT-MR-C & 2 & 0.0 & \sn{2.328}{-10} \\
      MCSA-ILUT-R-EV & 2 & 0.0 & \sn{2.328}{-10} \\
      MCSA-ILUT-MR-EV & 2 & 0.0 & \sn{2.328}{-10} \\
      \hline
      GMRES-ILUT & 3 & 0.0 & \sn{1.164}{-10} \\
      MCSA-ILUT-R-C & 3 & 0.0 & \sn{1.746}{-10} \\
      MCSA-ILUT-MR-C & 3 & 0.0 & \sn{2.256}{-9} \\
      MCSA-ILUT-R-EV & 3 & 0.0 & \sn{2.801}{-10} \\
      MCSA-ILUT-MR-EV & 3 & 0.0 & \sn{2.256}{-10} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      4-group fuel assembly problem.} \textit{The maximum and minimum
      absolute differences over the entire spatial domain are
      presented with BiCGStab used as the reference. Each calculation
      was converged with the same eigensolver and linear solver
      tolerances.}}
  \label{tab:serial_differences_g4}
\end{table}
